Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
Added experimental setup.

\section{Experimental Setup}
\begin{verbatim}
+( ) What do we want to demonstrate? Software pipelining can improve the
     performance even on Out-of-order machines.

@@

+( ) We want to show the breakdown of the cycles for each test and where the
     stalls were occurring.
+( ) What is our testbed? What machines do we use?
\end{verbatim}

@@

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_xeon_e5320.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Xeon E5320.}
\label{fig:gemv_corei7}
\end{figure}

>>>>

\section{Experimental Setup}
\begin{comment}
+( ) What do we want to demonstrate? Software pipelining can improve the
     performance even on Out-of-order machines.

@@

+( ) What is our testbed? What machines do we use?
\end{comment}

The goal of our experiments is to demonstrate the effectiveness of software
pipelining at the C code level for automatically generated numerical
operations. Instruction scheduling is one of the few optimizations that expert
has over SPIRAL. Thus, showing that software pipelining in addition to loop
unrolling outperforms unrolling alone will help in bridging the gap between
experts and APGS like SPIRAL.

%% NOTE: need to explain this WAY better in the future.
For our experiments we benchmarked multiple variants of Matrix-Vector(GEMV) on
several systems with different microarchitectures. The variants included a
baseline in which no loops were unrolled, two unrolled variants where the
inner-most loop was fully unrolled and the other dimension was unrolled by
either 1 or 4. Additionally, there were two variants that were software pipelined
versions of the unrolled code. The two different unrollings resulted in
completely different schedules in the software pipelined code. It is worth
noting that we specifically chose our input sizes to fit entirely in the L1
cache, so that performance would mostly be impacted by the number of
instruction stalls.

%% NOTE: in future, need actual parameters on these systems.
The systems we tested on were selected for their varied scheduling
facilities with respect to instruction window size where applicable. We chose three
out-of-order architectures (Core i7 960, Core2 X9650, Xeon E5320) and a single
in-order system (Intel Atom).

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=.5]{gemv_xeon_e5320.png}
\end{center}
\caption{Relative speedup of GEMV on the Intel Xeon E5320.}
\label{fig:gemv_xeon}
\end{figure}

@@
